\mytitle{My desire to strengthen our relationship}

There are several times that we heard and saw cool quotes in TV or on the internet. They are usually good to motivate or to guide your life. But please be aware that nothing are absolutely perfect. One quote that people usually uses to guide our relationship says something like "Be yourself. If your boyfriend want you to change, it means that he doesn't love you anymore". I really agree with this quote becauses it make sense. However it's not perfectly practical. For example, in the beginning of our relationship, we had a lot arguments and we didn't listen to each other that much. Is it ok if we are still the same?

Sometimes, I don't know what to do with concept "Enjoy our time that we can stay together as much as possible". One question that always popped up in my mind is "what will happen after that?". Should I care how our relationship will be after that? What will happen if we have arguments? It's harder to solve the problem when we are far way. Sometimes, hugging or kissing can solve our issues but those cannot be done when we are far away. It's harder to guess what the other side is thinking when we can only hear his/her voice. Should I try to reduce the effect of our arguments? 

What happened in the past usually will happen in the future. Do you believe that a guy who keep nagging can suddenly stop nagging? Do you believe that a guy who want to sleep a lot can suddenly change his habit? Do you believe a girl who have a habit of carrying/buying a lot of shoes can stop this maniac? Do you believe a girl who always gossip other people can stop not to gossip you? Yes, that can happen but it need a strong reason/motivation to change. It's the same for our relationship. It's not hard at all to predict what will happen to us in the future from what happened in the past. Do you remember your conversation with Sherwin that you told him that we were broken up and sherwin said "it's normal"?. He knows that because you said "we are broken up now" to him for tons of times and our relation returned to normal in the very next day. It's the same for the arguments when we were far away due to several causes. It's definitely will happen in the future.

Because of that, I really don't like the sentence "Why do you always bring up our arguments in the past? Why don't we just enjoy our current happiness?". The reason is it'll likely to happen in the future. My dislike also goes for what you said last night, Nov 12, "It not happen yet. Please don't concern about it". At which moment that we can talk? At which moment that we should find the way to prevent this kind of stuffs? I tried to find the way and method to talk to you but it rarely worked.

Anyway, I also respect your opinion. I believe that you should have a good reason for what you did. I'll use your method to maintain our relationship. I'll do what I should do. I will not care what happened in the past. I'll also not care what will happen in the future. I'll enjoy today happiness as much as possible.

Please forgive me for what I did. I only want to make our relationship as strong as possible. I also want you to be happy as much as possible as well.

